%!TEX TS-program = xelatex
%!TEX encoding = UTF-8 Unicode
% Awesome CV LaTeX Template for CV/Resume
%
% This template has been downloaded from:
% https://github.com/posquit0/Awesome-CV
%
% Author:
% Claud D. Park <posquit0.bj@gmail.com>
% http://www.posquit0.com
%
% Template license:
% CC BY-SA 4.0 (https://creativecommons.org/licenses/by-sa/4.0/)
%


%-------------------------------------------------------------------------------
% CONFIGURATIONS
%-------------------------------------------------------------------------------
% A4 paper size by default, use 'letterpaper' for US letter
\documentclass[11pt, a4paper]{awesome-cv}

% Configure page margins with geometry
\geometry{left=1.4cm, top=.8cm, right=1.4cm, bottom=1.8cm, footskip=.5cm}

% Specify the location of the included fonts
\fontdir[fonts/]

% Color for highlights
% Awesome Colors: awesome-emerald, awesome-skyblue, awesome-red, awesome-pink, awesome-orange
%                 awesome-nephritis, awesome-concrete, awesome-darknight
\colorlet{awesome}{awesome-darknight}
% Uncomment if you would like to specify your own color
% \definecolor{awesome}{HTML}{CA63A8}

% Colors for text
% Uncomment if you would like to specify your own color
% \definecolor{darktext}{HTML}{414141}
% \definecolor{text}{HTML}{333333}
% \definecolor{graytext}{HTML}{5D5D5D}
% \definecolor{lighttext}{HTML}{999999}

% Set false if you don't want to highlight section with awesome color
\setbool{acvSectionColorHighlight}{false}

% If you would like to change the social information separator from a pipe (|) to something else
\renewcommand{\acvHeaderSocialSep}{\quad\textbar\quad}


%-------------------------------------------------------------------------------
%	PERSONAL INFORMATION
%	Comment any of the lines below if they are not required
%-------------------------------------------------------------------------------
% Available options: circle|rectangle,edge/noedge,left/right
% \photo[rectangle,edge,right]{./examples/profile}
\name{João}{da Silva Fernandes}

\mobile{(+351) 917456174}
\email{hi@joaofernandes.me}
\homepage{joaofernandes.me}
\github{JSFernandes}
\linkedin{jsfernandes}

%-------------------------------------------------------------------------------
\begin{document}

% Print the header with above personal informations
% Give optional argument to change alignment(C: center, L: left, R: right)
\makecvheader[C]

% Print the footer with 3 arguments(<left>, <center>, <right>)
% Leave any of these blank if they are not needed
\makecvfooter
  {\today}
  {João Fernandes~~~·~~~Résumé}
  {\thepage}


%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Summary}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cvparagraph}

%---------------------------------------------------------
Full stack web developer with 7 years of experience, most of it being with Ruby on Rails.
Worked at startups, at a big company, and currently working as a freelance contractor.
\end{cvparagraph}


%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Work Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}


%---------------------------------------------------------
  \cventry
    {Senior Software Engineer - Contractor} % Job title
    {\href{https://quaderno.io/}{Quaderno}} % Organization
    {Remote} % Location
    {Oct. 2020 - Present}
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Reduced test build time by 50\%.}
        \item {Diagnosed and resolved memory issues which caused CI builds and deploys to become stuck.}
        \item {Introduced integration tests with Capybara and Selenium.}
        \item {Implemented two factor authentication.}
        \item {Improved performance for public API endpoints by reducing and optimising database operations.}
        \item {Introduced continuous delivery via feature flags.}
        \item {Encrypted customer personal information in the database using the AES-GCM algorithm.}
        \item {Technologies used: Ruby on Rails, MySQL, Redis, ElasticSearch, Stimulus, Coffeescript, Sidekiq, RSpec, Capybara, NewRelic, SemaphoreCI}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Senior Software Engineer - Contractor} % Job title
    {\href{https://www.fetlife.com/}{Fetlife}} % Organization
    {Remote} % Location
    {Jan. 2020 - Oct. 2020}
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Integrated the website's content and user reporting functionality with Help Scout.}
        \item {Expanded the functionality of a user blocking another one to be reflected in all areas of the website, including comments on content of users unrelated to the block, and mentions of the blocked user.}
        \item {Improved the integration between the repository containing the main application and another repository with the community guidelines defined in YAML to make user and content reporting more configurable by the moderation team.}
        \item {Implemented redesigned responsive versions of existing pages, including image and video upload pages.}
        \item {Technologies used: Ruby on Rails, Vue.js, Typescript, MySQL, Redis, ElasticSearch, Sidekiq, Kubernetes, RSpec, Sentry, NewRelic, CircleCI}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Part-Time Contractor} % Job title
    {\href{https://flowifyaccounting.com/}{Flowify Accounting}} % Organization
    {Remote} % Location
    {Sep. 2019 - Feb. 2020} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Updated user onboarding experience and e-mails.}
        \item {Added user tracking with Segment.io}
        \item {Added functionality to automatically generate invoices and track inventory items in QuickBooks Online based on sales made on Shopify.}
        \item {Technologies used: Ruby on Rails, PostgreSQL, Heroku}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Part-Time Contractor} % Job title
    {\href{https://www.saintfriend.co/}{Saint Friend}} % Organization
    {Remote} % Location
    {Sep. 2019 - Oct. 2019} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Added a new page to the marketing website of one of the agency's clients.}
        \item {Technologies used: Jekyll, SCSS, Javascript, Youtube API, Aerobatic}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Senior Software Engineer} % Job title
    {\href{https://www.xing.com/}{Xing}} % Organization
    {Barcelona, Spain} % Location
    {Nov. 2017 - Dec. 2019} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Implemented image and video updates for company profiles.}
        \item {Implemented GDPR compliance on B2B services.}
        \item {Introduced a test driven culture in the React codebase.}
        \item {Collaborated in developing a design system library to ensure design consistency among the various products.}
        \item {Migrated legacy Backbone.js code written in Coffeescript to React code written in Javascript.}
        \item {Mentored junior developers following their graduation from a coding bootcamp.}
        \item {Technologies used: Ruby on Rails, MySQL, React, Styled Components, Jest, React Testing Library, Cypress, RabbitMQ, Docker, Kubernetes, RSpec, Capybara, Jenkins, Sentry}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Senior Software Engineer} % Job title
    {\href{https://novicap.com/}{Novicap}} % Organization
    {Barcelona, Spain} % Location
    {Jun. 2017 - Oct. 2017} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Migrated an existing double entry accounting system to a more flexible one that solved existing un-resolvable loans. This system supported loans with multiple lenders and processed all the associated payouts depending on the payment date.}
        \item {Implemented accounting reports for the entire platform and for individual lenders.}
        \item {Technologies used: Ruby on Rails, React, RSpec, PostgreSQL, AWS}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Pro Bono Consultant} % Job title
    {\href{https://movingworlds.org/}{Moving Worlds}} % Organization
    {Medellin, Colombia \& remote} % Location
    {Feb. 2017 - Dec. 2017} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Took over maintenance and development of the unmaintained website.}
        \item {Fixed critical issues in the admin workflow and in the integration with Mailchimp.}
        \item {Improved performance of listings by performing pagination in the server rather than the browser.}
        \item {Helped hire and onboard a Director of Engineering.}
        \item {Technologies used: Node.js, Express, Sequelize, PostgreSQL, Docker, AWS, Mailchimp}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Software Engineer} % Job title
    {\href{https://www.seedrs.com/}{Seedrs}} % Organization
    {Lisbon, Portugal \& London, UK} % Location
    {Aug. 2014 - Dec. 2016} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Worked on a site-wide responsive redesign.}
        \item {Worked on financial and legal requirements imposed by the UK’s FCA.}
        \item {Integrated the website with Salesforce for to improve the process of the marketing and operation teams.}
        \item {Worked on improving the performance of the investment process, so that more investments could be made per minute.}
        \item {Re-implemented the accounting process for delivering funds to entrepreneurs, so it could be done in batches with correct fee and profit calculations.}
        \item {Technologies used: Ruby on Rails, MySQL, RSpec, Capybara, SCSS, jQuery, Ember.js, MongoDB, Stripe, Intercom, Salesforce, Mixpanel, NewRelic}
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}

%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Education}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {M.Sc. in Computer Software Engineering} % Degree
    {Faculty of Engineering of the University of Porto} % Institution
    {Porto, Portugal} % Location
    {Sep. 2009 - Jul. 2014} % Date(s)
    {
      \begin{cvitems} % Description(s) bullet points
        \item {Created a Javascript library to interact with webpages using the Microsoft Kinect as part of the Master's Thesis, in collaboration with Glintt Healthcare Solutions.}
        \item {Studied in Sapienza Università di Roma during one semester under the Erasmus programme.}
        \item {Managed the programme for the 2013 edition of Portugal's national meeting of IT students, which was hosted in Porto.}
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}


%-------------------------------------------------------------------------------
\end{document}
